Generalized Plackett-Luce Likelihoods

### 2022-08-17 inst/jss_hyper3.Rnw
the loser

which has a minimum of about $13.9$ at at about $a=0.575$.  This is
intermediate between the two-runner case where the Fisher information
exceeds 4 (minimum at $p_a=\frac{1}{2}$), and the case of three
distinct runners, where the Fisher information exceeds
$\frac{1323}{16}\simeq 82.7$ (minimum at $p_a=p_b=p_c=\frac{1}{3}$); a
brief discussion is given at \code{inst/fisher\_inf\_PL3.Rmd}.

>>>>

which has a minimum of about $13.9$ at at about $a=0.575$.  We can
compare this with the Fisher information ${\mathcal I}$ for the case
of three distinct runners $a,b,c$, evaluated at its minimum of
$p_a=p_b=p_c=\frac{1}{3}$.  If we observe the complete order
statistic, ${\mathcal I}=\frac{1323}{16}\simeq 82.7$; if we observe
just the winner, ${\mathcal I}=27$, and if we observe just the loser
we have ${\mathcal I}=\frac{16875}{256}\simeq 65.9$.  A brief
discussion is given at \code{inst/fisher\_inf\_PL3.Rmd}.
